Cascades, Product Conversion, Whatever

### 2012-12-11 paper.tex
Cropped cloud_n10_r05_log.pdf to make diagram better
Added a few changes, really just premerge commit

\section{Problem Statement}
\label{prob_statement}
We propose studying a simple cascade model over an arbitrary social
network. In this model each agent is represented by a node in a graph
and all of their friends / neighbors are represented by edges in the
same graph. Over the course of the game each agent will make an
irreversible choice between one of two types ($Y$ or $N$) -- where
agents that prefer $Y$ are less frequent -- and will get a payoff at
the end of the game corresponding to the number of neighbors that
chose the same type as well as a bonus if they chose their prefered
type. Thus each agent is torn between choosing their prefered type and
choosing the type that a majority of their neighbors chose. The game
is played with a single node making a choice between types at each
point in time. We are looking to choose an order or schedule over
agents to maximize the number of minority ($Y$) choices. We are
interested in two different classes of schedules, offline and
online. Offline schedules must schedule the entire set of agents
before the game is played, whereas online schedules can be revised as
agents make their decisions. We are interested in the difference
between the optimal number of minority types chosen when the agents
behave myopically, meaning their choice optimizes their current
payoff, and when the agents behave strategically, meaning their choice
optimizes their expected payoff at the end of the game. Strategic
agents vary significantly depending on how much information they
have. Here we assume they know the entire graph structure, every other
agents strategy, the probability of an agent’s type, all decided
node's choices, and the schedule.

@@

>>>>

\section{Problem Statement}
\label{prob_statement}

We propose studying a simple cascade model over an arbitrary social
network. In this model each agent is represented by a node in a graph
and all of their friends / neighbors are represented by edges in the
same graph. Over the course of the game each agent will make an
irreversible choice between one of two types ($Y$ or $N$) -- where
agents that prefer $Y$ are less frequent -- and will get a payoff at
the end of the game corresponding to the number of neighbors that
chose the same type as well as a bonus if they chose their prefered
type. Thus each agent is torn between choosing their prefered type and
choosing the type that a majority of their neighbors chose. The game
is played with a single node making a choice between types at each
point in time. We are looking to choose an order or schedule over
agents to maximize the number of minority ($Y$) choices. We are
interested in two different classes of schedules, offline and
online. Offline schedules must schedule the entire set of agents
before the game is played, whereas online schedules can be revised as
agents make their decisions. We are interested in the difference
between the optimal number of minority types chosen when the agents
behave myopically, meaning their choice optimizes their current
payoff, and when the agents behave strategically, meaning their choice
optimizes their expected payoff at the end of the game. Strategic
agents vary significantly depending on how much information they
have. Here we assume they know the entire graph structure, every other
agents strategy, the probability of an agent’s type, all decided
node's choices, and the schedule.

@@

Patterns may not exist, but there may still be order level
relationships / bounds that are possible.

See if we can prove the problem is PPAD or NP-complete.
